The Topic Browser\\An Interactive Tool for Browsing Topic Models

### 2010-10-24 masters_thesis/browser_nips/paper.tex
Fixed a few things with the authors
Some minor revisions

\title{The Topic Browser\\An Interactive Tool for Browsing Topic Models}
\author{
Matthew J. Gardner \\
Department of Computer Science \\
Brigham Young University \\
\texttt{mjg82@byu.edu} \\
\And
Joshua Lutes \\
Department of Computer Science \\
Brigham Young University \\
\texttt{joshua@lutes.me} \\
\And
Jeff Lund \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jefflund@gmail.com} \\
\And
Josh Hansen \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jjfresh@byu.edu} \\
\And
Dan Walker \\
Department of Computer Science \\
Brigham Young University \\
\texttt{danwalkeriv@gmail.com} \\
\And
Eric Ringger \\
Department of Computer Science \\
Brigham Young University \\
\texttt{ringger@cs.byu.edu} \\
\And
Kevin Seppi \\
Department of Computer Science \\
Brigham Young University \\
\texttt{kseppi@lcs.byu.edu} \\
}

@@

To aid in the visualization of topic models and in pattern discovery in
document collections, we present The Topic Browser, a web-based tool for
interactively exploring both the output of a topic modeling algorithm and its
attendant corpus.  Our topic browser incorporates many visualizations of topic
models previously published as well as some innovative ideas of our own.  The
Topic Browser is an aid both to those who wish to browse through a corpus and
for those who wish to analyze the topic model itself.  We believe that this
interactive approach to visualization in browsing reveals topics and topical
trends in large document collections in a way that is not possible with static
visualizations.  The rest of this paper describes the Topic Browser in an
attempt to demonstrate that this is tool.  We display our tool with a topic
model run using MALLET's implementation of LDA~\cite{mallet} with 150 topics on
a collection of about 460 campaign speeches from the 2008 presidential primary
and general elections retrieved from http://2008election.procon.org.

@@

In order to browse more effectively through topics, we introduce topic metrics
that give information about the topic.  These range from simple metrics, such
as the number of words tokens and types labeled with the topic, to more
complicated metrics such as how dispersed the topic is across documents, or how
coherent its words
are~\cite{newman-2010-automatic-evaluation-of-topic-coherence}.  We also use
pairwise topic metrics as similarity measures to show similar topics.

>>>>

\title{The Topic Browser\\An Interactive Tool for Browsing Topic Models}
\author{
Matthew J. Gardner \\
Department of Computer Science \\
Brigham Young University \\
\texttt{mjg82@byu.edu} \\
\And
Joshua Lutes \\
Department of Computer Science \\
Brigham Young University \\
\texttt{joshua@byu.edu} \\
\And
Jeff Lund \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jefflund@gmail.com} \\
\And
Josh Hansen \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jjfresh@byu.edu} \\
\And
Dan Walker \\
Department of Computer Science \\
Brigham Young University \\
\texttt{danwalkeriv@gmail.com} \\
\And
Eric Ringger \\
Department of Computer Science \\
Brigham Young University \\
\texttt{ringger@cs.byu.edu} \\
\And
Kevin Seppi \\
Department of Computer Science \\
Brigham Young University \\
\texttt{kseppi@cs.byu.edu} \\
}

@@

To aid in the visualization of topic models and in pattern discovery in
document collections, we present The Topic Browser, a web-based tool for
interactively exploring both the output of a topic modeling algorithm and its
attendant corpus.  Our topic browser incorporates many visualizations of topic
models previously published as well as some innovative ideas of our own.  The
Topic Browser is an aid both to those who wish to browse through a corpus and
for those who wish to analyze the topic model itself.  We believe that this
interactive approach to visualization in browsing reveals topics and topical
trends in large document collections in a way that is not possible with static
visualizations.  The rest of this paper describes the Topic Browser in an
attempt to demonstrate that this is true.  We display our tool with a topic
model run using MALLET's implementation of LDA~\cite{mallet} with 150 topics on
a collection of about 460 campaign speeches from the 2008 presidential primary
and general elections retrieved from http://2008election.procon.org.

@@

In order to browse more effectively through topics, we introduce topic metrics
that give information about the topic.  These range from simple metrics, such
as the number of word tokens and types labeled with the topic, to more
complicated metrics such as how dispersed the topic is across documents, or how
coherent its words
are~\cite{newman-2010-automatic-evaluation-of-topic-coherence}.  We also use
pairwise topic metrics as similarity measures to show similar topics.
